### 2015-09-30 paper/main.tex
simplify model description

Here we consider an Empirical Bayes (EB) approach to FDR. This idea is, of course, far from new:
indeed, the notion that EB approaches could be helpful in handling multiple comparisons predates introduction of
the FDR  (e.g.~\cite{greenland1991empirical}). More recently, EB approaches to the FDR
have been extensively studied by several authors, 
especially B.~Efron and co-authors 
\cite{efron2001empirical, efron2002empirical,efron2003robbins,efron2008microarrays,efron2010large}; 
see also \cite{kendziorski2003parametric,newton2004detecting, 
datta2005empirical,muralidharan2010empirical} for example.
So what is the ``New Deal" here? We introduce two simple ideas that are new (at least compared with
existing widely-used FDR pipelines) and can substantially affect
inference. The first idea is to {\it assume that the distribution of effects is unimodal}, and to perform
non-parametric inference under this assumption. This yields a very simple, fast, and stable computer implementation,
 and improves inference of FDR, at least when the unimodal assumption is correct.  
The second idea is to use two numbers -- effect sizes, and their standard errors -- rather than just one -- $p$ values, or $z$ scores -- 
to summarize each measurement. This idea allows variations in measurement precision to be accounted for,
 and avoids the problem with standard pipelines that poor-precision measurements can inflate estimated FDR.

@@

Our methods are implemented in an R package, \ashr (for {\bf a}daptive {\bf sh}rinkage in {\bf R}), available at \url{http://github.com/stephens999/ashr}.

@@

 \subsection*{Outline}

% Here we consider one setting in which FDR-based methods are widely used:
%an experimenter has measured a large numbers of ``effects", each with an associated
%measurement precision (standard error), 
%and the goal is to identify which of the effects we can declare to be non-zero, with some prescribed level of confidence.
%Although the usual focus of FDR-based methods is on distinguishing zero and non-zero effects,
%here we also focus on providing estimates -- both point estimates and interval estimates -- for these effects.
%This setting arises commonly in many areas of statistics, and particularly in genomics applications.
%For example, in genomics
%a common goal is to identify ``differentially-expressed genes" -- that is, genes
%whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
%mean expression level between the two conditions, often referred to as the ``log-fold change". 
We begin by presenting the simplest version of method, and comparing it with existing work, before detailing further embellishments.

Suppose that we are interested in the values of $J$ ``effects" $\beta=(\beta_1,\dots,\beta_J)$. For example, in a typical genomics application
that aims to identify differentially expressed genes,  $\beta_j$ might be the difference in the mean (log) expression of gene $j$ in two conditions.
In contexts where FDR methods are applied, interest often focuses on identifying significant non-zero effects;
that is, in testing the null hypotheses $H_j:\beta_j=0$.  Here we will also tackle
the more general problem of estimating, and assessing uncertainty in, the effect sizes $\beta_j$.

We assume that the available data are estimates $\bhat=(\bhat_1,\dots,\bhat_J)$ of these effects,
and corresponding (estimated) standard errors $\shat=(\shat_1,\dots,\shat_J)$.  Our goal is to compute a posterior distribution for $\beta$ given the observed data $\bhat,\shat$,
which by Bayes theorem can be written as 
\begin{equation}
p(\beta | \bhat, \shat) \propto p(\beta | \shat) p(\bhat | \beta, \shat).
\end{equation}

We assume that the observations $\bhat$ are conditionally independent given $\beta,\shat$, and that the distribution of
$\bhat_j$ depends only on the corresponding $\beta_j,\shat_j$, so
\begin{equation}
p(\bhat | \beta, \shat) = \prod_j p(\bhat_j | \beta_j, \shat_j).
\end{equation}
Initially we assume that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation,
\begin{equation} \label{eqn:normlik}
p(\bhat_j | \beta_j, \shat_j) =  N(\bhat_j; \beta_j, \shat^2_j),
\end{equation}
where $N(\cdot; \mu,\sigma^2)$ denotes the density of a normal distribution with mean $\mu$ and variance $\sigma^2$.

We assume that the (unobserved) effects $\beta_j$ come from some distribution $g$, which is to be estimated, and which we write 
as a mixture of null and alternative components:
\begin{equation} \label{eqn:betaj0}
g(\cdot) = \pi_0 \delta_0(\cdot) + (1-\pi_0) g_1(\cdot)
\end{equation}
where $\pi_0$ denotes the proportion of effects that are null, $\delta_0(\cdot)$ denotes a point mass at 0, and $g_1(\cdot)$ denotes the distribution of the non-zero $\beta_j$.
We also assume that (given $g$) the $\beta_j$ are independent, and independent of $\shat$ (a point we return to later), so
\begin{equation} \label{eqn:beta-iid}
p(\beta | \shat) = \prod_j g(\beta_j).
\end{equation}

Our key further assumption, which distinguishes our approach from previous EB approaches to FDR analysis, is that $g_1$ is unimodal,
with a mode at 0. One simple way to implement this ``Unimodal Assumption" (UA)  is
to use a mixture of zero-mean normal distributions:
\begin{equation} \label{eqn:mixnorm}
g_1(\cdot) = \sum_{k=1}^K w_k N(\cdot; 0, \sigma_k^2)
\end{equation}
where $N(\cdot; \mu,\sigma^2)$ denotes the density of a normal distribution with mean $\mu$ and standard deviation $\sigma$.
Here the $w_k$ are non-negative mixture weights that sum to $1$ and are to be estimated, and the component standard deviations $\sigma_1,\dots,\sigma_K$ 
represent a large and dense grid of fixed positive numbers spanning a range from very small to very big (so $K$ is fixed and large).
 The symmetry of the normal distribution implies that (\ref{eqn:mixnorm}) is not only unimodal, but also symmetric about zero. We introduce
 more flexible alternatives based on using mixtures of uniform distributions, and further details (such as choice of gridpoints $\{\sigma_k:k=1,\dots,K\}$) below.

 Substituting (\ref{eqn:mixnorm}) for $g_1$ in (\ref{eqn:betaj0}), and defining $\pi_k := (1-\pi_0)w_k$ for $k=1,\dots,K$ (and also $\sigma_k:=0$, and $N(\cdot;0,0):=\delta_0(\cdot)$)
 yields a notationally-convenient form for $g$, with hyperparameters $\pi:=(\pi_0,\pi_1,\dots,\pi_K)$ whose elements are non-negative and sum to 1:
 \begin{equation} \label{eqn:g}
 g(\cdot; \pi) = \sum_{k=0}^K \pi_k N(\cdot; 0, \sigma_k^2).
 \end{equation}

 Putting all this together, and making the dependence on hyperparameters $\pi$ explicit, we have:
 \begin{align} \label{eqn:betaj}
 p(\beta | \shat, \pi) & = \prod_j g(\beta_j; \pi), \\  \label{eqn:normlik2}
 p(\bhat | \beta, \shat, \pi) &= \prod_j N(\bhat_j; \beta_j, \shat_j^2), 
 \end{align}
 with $g$ given by the mixture of normals $(\ref{eqn:g})$.

In words, the effects $\beta_j$ are independent and identically distributed from a mixture of zero-centered normal distributions, and 
each observation $\bhat_j$ is a noisy measurement of $\beta_j$ with standard error $\shat_j$.
 Together, these assumptions imply that the observations $\bhat_j$ are also independent observations, each from a mixture of normal distributions:
\begin{equation} \label{eqn:marginallik}
p(\bhat | \shat, \pi) =   \prod_j  [\sum_{k=0}^K \pi_k N(\bhat_j; 0, \sigma_k^2 + \shat_j^2)].
\end{equation}

@@

In practice we make a small modification to this procedure: instead of obtaining $\hat\pi$ by maximizing the likelihood, we instead maximise a penalized
likelihood, where the penalty encourages $\hat\pi_0$ to be as big as possible whilst remaining consistent with the observed data (see details below). 
We introduce this penalty because in FDR appllications it is considered desirable to avoid underestimating $\pi_0$ so as to avoid underestimating the FDR.

@@

Using a mixture of zero-centered normal distributions for $g$ in (\ref{eqn:g}) implies that $g$ is not only unimodal, but also symmetric.
Furthermore, even some symmetric unimodal distributions, such as those with a flat top, cannot be well approximated by a mixture of zero-centered normals.
 Therefore, we have implemented a more general approach, based on 
\begin{equation} \label{eqn:g-general}
g(\cdot; \pi) = \sum_{k=0}^K \pi_k f_k(\cdot) 
\end{equation}
where $f_0$ is a point mass on 0, and $f_k$ ($k=1,\dots,K$) are pre-specified component distributions with one of the following forms: 
\begin{enumerate}[(i)]
\item $f_k(\cdot) = N(\cdot; 0, \sigma^2_k)$,
\item $f_k(\cdot) = U[\cdot; -a_k,a_k]$,
\item $f_k(\cdot) = U[\cdot; -a_k,0] \text{ and/or } U[\cdot; 0,a_k]$,
\end{enumerate}
where $U[\cdot; a,b]$ denotes the density of a uniform distribution on $[a,b]$.
(In (iii) we include both components in the mixture (\ref{eqn:g}), so a grid of values $a_1,\dots,a_K$ defines $2K+1$ mixture component densities, 
and $\pi$ is a $2K+1$ vector that sums to 1.)
The simplest version (\ref{eqn:g}) corresponds to (i).
Replacing these with uniform components (ii)-(iii) only slightly complicates calculations
under the normal likelihood (\ref{eqn:normlik}), and greatly simplifies the calculations under the $t$ likelihood
(\ref{eqn:tlik}) introduced below. The use of uniform components here closely mirrors \cite{cordy1997deconvolution}.
(In fact our implementation can handle {\it any} prespecified uniform or normal distributions for $f_k$ provided they are all from the same family;
however, we restrict our attention here to (i)-(iii) which imply a unimodal $g$.)

Moving from (i) to (iii) the representation (\ref{eqn:g}) becomes increasingly flexible. Indeed,
using a large dense grid of $\sigma^2_k$ or $a_k$, we can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[(i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in  high-dimensional regression settings.
\item any symmetric unimodal distribution about 0.
\item any unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to \cite{khintchine1938unimodal} and  \cite{shepp1962symmetric}; see \cite{feller1971introduction}, p158. 
In other words, (ii) and (iii) provide fully non-parametric estimation for $g$ under the constraints that it is (ii) both unimodal and symmetric, or (iii) unimodal only.

>>>>

Here we consider an Empirical Bayes (EB) approach to FDR. This idea is, of course, far from new:
indeed, the notion that EB approaches could be helpful in handling multiple comparisons predates introduction of
the FDR  (e.g.~\cite{greenland1991empirical}). More recently, EB approaches to the FDR
have been extensively studied by several authors, 
especially B.~Efron and co-authors 
\cite{efron2001empirical, efron2002empirical,efron2003robbins,efron2008microarrays,efron2010large}; 
see also \cite{kendziorski2003parametric,newton2004detecting, 
datta2005empirical,muralidharan2010empirical} for example.
So what is the ``New Deal" here? We introduce two simple ideas that are new (at least compared with
existing widely-used FDR pipelines) and can substantially affect
inference. The first idea is to {\it assume that the distribution of effects is unimodal}. This yields a very simple, fast, and stable computer 
implementation, as well as improving inference of FDR when the unimodal assumption is correct.  
The second idea is to use two numbers -- effect sizes, and their standard errors -- rather than just one -- $p$ values, or $z$ scores -- 
to summarize each measurement. This idea allows variations in measurement precision to be better accounted for,
 and avoids a problem with standard pipelines that poor-precision measurements can inflate estimated FDR.

@@

Our methods are implemented in an R package, \ashr (for {\bf a}daptive {\bf sh}rinkage in {\bf R}), available at \url{http://github.com/stephens999/ashr}.
(We address the reasons for this name, and connections with shrinkage analysis, in the Discussion.)

@@

 \subsection*{Model Outine}

% Here we consider one setting in which FDR-based methods are widely used:
%an experimenter has measured a large numbers of ``effects", each with an associated
%measurement precision (standard error), 
%and the goal is to identify which of the effects we can declare to be non-zero, with some prescribed level of confidence.
%Although the usual focus of FDR-based methods is on distinguishing zero and non-zero effects,
%here we also focus on providing estimates -- both point estimates and interval estimates -- for these effects.
%This setting arises commonly in many areas of statistics, and particularly in genomics applications.
%For example, in genomics
%a common goal is to identify ``differentially-expressed genes" -- that is, genes
%whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
%mean expression level between the two conditions, often referred to as the ``log-fold change". 
We begin with the simplest version of our method, and compare it with existing work, before detailing embellishments.

Suppose that we are interested in the values of $J$ ``effects" $\beta=(\beta_1,\dots,\beta_J)$. For example, in a typical genomics application
that aims to identify differentially expressed genes,  $\beta_j$ might be the difference in the mean (log) expression of gene $j$ in two conditions.
In contexts where FDR methods are applied, interest often focuses on identifying ``significant" non-zero effects;
that is, in testing the null hypotheses $H_j:\beta_j=0$.  Here we tackle both this problem, and the  
more general problem of estimating, and assessing uncertainty in, $\beta_j$.

Assume that the available data are estimates $\bhat=(\bhat_1,\dots,\bhat_J)$ of the effects,
and corresponding (estimated) standard errors $\shat=(\shat_1,\dots,\shat_J)$.  Our goal is to compute a posterior distribution for $\beta$ given the observed data $\bhat,\shat$,
which by Bayes theorem can be written as 
\begin{equation}
p(\beta | \bhat, \shat) \propto p(\beta | \shat) p(\bhat | \beta, \shat).
\end{equation}

For $p(\beta | \shat)$ we assume that the $\beta_j$ are independent from a unimodal distribution $g$.
This unimodal assumption (UA) is a key assumption that distinguishes our approach from previous EB approaches to FDR analysis.
A simple way to implement the UA is to assume that $g$ is
a mixture of a point mass at 0 and a mixture of {\it zero-mean} normal distributions:
\begin{align} \label{eqn:beta}
p(\beta | \shat, \pi) & = \prod_j g(\beta_j; \pi), \\   
g(\cdot; \pi) & = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k N(\cdot; 0, \sigma_k^2), \label{eqn:mixnorm}
\end{align}
where $N(\cdot; \mu, \sigma^2)$ denotes the density of the normal distribution with mean $\mu$ and variance $\sigma^2$.
Here the mixture proportions $\pi=(\pi_0,\dots,\pi_K)$ are hyperparameters, which are non-negative and sum to one, and are to be estimated,
while the mixture component standard deviations $\sigma_1,\dots,\sigma_K$ 
represent a large and dense grid of {\it fixed} positive numbers spanning a range from very small to very big (so $K$ is fixed and large). 
(We encourate the reader to think of this grid as becoming infinitely large and dense, as a non-parametric limit,
although of course in practice we use a finite grid -- see Implementation Details.)

For the likelihood $p(\bhat | \beta, \shat)$ we assume  
\begin{equation} \label{eqn:normlik}
p(\bhat | \beta, \shat) = \prod_j N(\bhat_j; \beta_j, \shat_j^2).
\end{equation}
Here, in additional to some conditional independence assumptions, we are 
effectively  assuming that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation.

This simple model features both the key ideas we want to emphasise in this paper: the UA is encapsulated in (\ref{eqn:mixnorm}) while
the different measurement precision of different observations is encapsulated in the likelihood (\ref{eqn:normlik}) -- specifically, observations
with larger standard error will have a flatter likelihood, and therefore have less impact on inference.
However, this simple model also has several additional assumptions that can be relaxed. Specifically,
\begin{enumerate}
\item  The use of a mixture of zero-mean normals (\ref{eqn:mixnorm}) also implies that $g$ is symmetric about 0; more flexibility can be obtained by replacing the mixture of normals with mixtures of uniforms [see (\ref{eqn:g-general})].
\item The model (\ref{eqn:beta}) assumes that the effects are identically distributed, independent of their standard errors $\shat$.
We can relax this to allow for a relationship between these quantities [see (\ref{eqn:beta-alpha})].
\item The likelihood (\ref{eqn:normlik}) effectively assumes that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation. We can generalize this likelihood using a $t$ likelihood [see (\ref{eqn:tlik})].
\end{enumerate}
Of course there remain limitations that are harder to relax, most notably the independence and conditional independence assumptions encapsulated in our model
(which are also made by most existing EB approaches to this problem). Correlations among tests certainly arise in practice, either due to genuine correlations
in the system of study, or due to unmeasured confounders, and their potential to impact results of an FDR analysis is important to consider
whatever analysis methods are used: see \cite{efron2007correlation,leek:2007} for relevant discussion.

%We assume that the observations $\bhat$ are conditionally independent given $\beta,\shat$, and that the distribution of
%$\bhat_j$ depends only on the corresponding $\beta_j,\shat_j$, so
%\begin{equation}
%p(\bhat | \beta, \shat) = \prod_j p(\bhat_j | \beta_j, \shat_j).
%\end{equation}
%Initially we assume that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation,
%\begin{equation} \label{eqn:normlik}
%p(\bhat_j | \beta_j, \shat_j) =  N(\bhat_j; \beta_j, \shat^2_j),
%\end{equation}
%where $N(\cdot; \mu,\sigma^2)$ denotes the density of a normal distribution with mean $\mu$ and variance $\sigma^2$.
%
%We assume that the (unobserved) effects $\beta_j$ come from some distribution $g$, which is to be estimated, and which we write 
%as a mixture of null and alternative components:
%\begin{equation} \label{eqn:betaj0}
%g(\cdot) = \pi_0 \delta_0(\cdot) + (1-\pi_0) g_1(\cdot)
%\end{equation}
%where $\pi_0$ denotes the proportion of effects that are null, $\delta_0(\cdot)$ denotes a point mass at 0, and $g_1(\cdot)$ denotes the distribution of the non-zero $\beta_j$.
%We also assume that (given $g$) the $\beta_j$ are independent, and independent of $\shat$ (a point we return to later), so
%\begin{equation} \label{eqn:beta-iid}
%p(\beta | \shat) = \prod_j g(\beta_j).
%\end{equation}
%
%Our key further assumption, which distinguishes our approach from previous EB approaches to FDR analysis, is that $g_1$ is unimodal,
%with a mode at 0. One simple way to implement this ``Unimodal Assumption" (UA)  is
%to use a mixture of zero-mean normal distributions:
%\begin{equation} \label{eqn:mixnorm}
%g_1(\cdot) = \sum_{k=1}^K w_k N(\cdot; 0, \sigma_k^2)
%\end{equation}
%where $N(\cdot; \mu,\sigma^2)$ denotes the density of a normal distribution with mean $\mu$ and standard deviation $\sigma$.
%Here the $w_k$ are non-negative mixture weights that sum to $1$ and are to be estimated, and the component standard deviations $\sigma_1,\dots,\sigma_K$ 
%represent a large and dense grid of fixed positive numbers spanning a range from very small to very big (so $K$ is fixed and large).
% The symmetry of the normal distribution implies that (\ref{eqn:mixnorm}) is not only unimodal, but also symmetric about zero. We introduce
% more flexible alternatives based on using mixtures of uniform distributions, and further details (such as choice of gridpoints $\{\sigma_k:k=1,\dots,K\}$) below. 
% 
% Substituting (\ref{eqn:mixnorm}) for $g_1$ in (\ref{eqn:betaj0}), and defining $\pi_k := (1-\pi_0)w_k$ for $k=1,\dots,K$ (and also $\sigma_k:=0$, and $N(\cdot;0,0):=\delta_0(\cdot)$)
% yields a notationally-convenient form for $g$, with hyperparameters $\pi:=(\pi_0,\pi_1,\dots,\pi_K)$ whose elements are non-negative and sum to 1:
% \begin{equation} \label{eqn:g}
% g(\cdot; \pi) = \sum_{k=0}^K \pi_k N(\cdot; 0, \sigma_k^2).
% \end{equation}
% 
% Putting all this together, and making the dependence on hyperparameters $\pi$ explicit, we have:
% \begin{align} \label{eqn:betaj}
% p(\beta | \shat, \pi) & = \prod_j g(\beta_j; \pi), \\  \label{eqn:normlik2}
% p(\bhat | \beta, \shat, \pi) &= \prod_j N(\bhat_j; \beta_j, \shat_j^2), 
% \end{align}
% with $g$ given by the mixture of normals $(\ref{eqn:g})$.

\subsection*{Fitting the model}

In words, the model above assumes that the effects $\beta_j$ are independent and identically distributed from a mixture of zero-centered normal distributions, and 
each observation $\bhat_j$ is a noisy measurement of $\beta_j$ with standard error $\shat_j$.
Together, these assumptions imply that the observations $\bhat_j$ are also independent observations, each from a mixture of normal distributions:
\begin{equation} \label{eqn:marginallik}
p(\bhat | \shat, \pi) =   \prod_j  [\sum_{k=0}^K \pi_k N(\bhat_j; 0, \sigma_k^2 + \shat_j^2)],
\end{equation}
where we define $\sigma_0:=0$.

@@

In practice we make a small modification to this procedure: instead of obtaining $\hat\pi$ by maximizing the likelihood, we instead maximise a penalized
likelihood [see (\ref{eqn:penalty})], where the penalty encourages $\hat\pi_0$ to be as big as possible whilst remaining consistent with the observed data. 
We introduce this penalty because in FDR appllications it is considered desirable to avoid underestimating $\pi_0$ so as to avoid underestimating the FDR.

@@

Using a mixture of zero-centered normal distributions for $g$ in (\ref{eqn:mixnorm}) implies that $g$ is not only unimodal, but also symmetric.
Furthermore, even some symmetric unimodal distributions, such as those with a flat top, cannot be well approximated by a mixture of zero-centered normals.
 Therefore, we have implemented a more general approach, based on 
\begin{equation} \label{eqn:g-general}
g(\cdot; \pi) = \sum_{k=0}^K \pi_k f_k(\cdot) 
\end{equation}
where $f_0$ is a point mass on 0, and $f_k$ ($k=1,\dots,K$) are pre-specified component distributions with one of the following forms: 
\begin{enumerate}[(i)]
\item $f_k(\cdot) = N(\cdot; 0, \sigma^2_k)$,
\item $f_k(\cdot) = U[\cdot; -a_k,a_k]$,
\item $f_k(\cdot) = U[\cdot; -a_k,0] \text{ and/or } U[\cdot; 0,a_k]$,
\end{enumerate}
where $U[\cdot; a,b]$ denotes the density of a uniform distribution on $[a,b]$.
(In (iii) we include both components in the mixture (\ref{eqn:g-general}), so a grid of values $a_1,\dots,a_K$ defines $2K+1$ mixture component densities, 
and $\pi$ is a $2K+1$ vector that sums to 1.)
The simplest version (\ref{eqn:mixnorm}) corresponds to (i).
Replacing these with uniform components (ii)-(iii) only slightly complicates calculations
under the normal likelihood (\ref{eqn:normlik}), and greatly simplifies the calculations under the $t$ likelihood
(\ref{eqn:tlik}) introduced below. The use of uniform components here closely mirrors \cite{cordy1997deconvolution}.
(In fact our implementation can handle {\it any} prespecified uniform or normal distributions for $f_k$ provided they are all from the same family;
however, we restrict our attention here to (i)-(iii) which imply a unimodal $g$.)

Moving from (i) to (iii) the representation (\ref{eqn:g-general}) becomes increasingly flexible. Indeed,
using a large dense grid of $\sigma^2_k$ or $a_k$, we can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[(i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in  high-dimensional regression settings.
\item any symmetric unimodal distribution about 0.
\item any unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to \cite{khintchine1938unimodal} and  \cite{shepp1962symmetric}; see \cite{feller1971introduction}, p158. 
In other words, (ii) and (iii) provide fully non-parametric estimation for $g$ under the constraints that it is (ii) both unimodal and symmetric, or (iii) unimodal only.
